Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-12 Grassmannian_cells.tex
Gr's

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
For $1\le r\le n-1$, let $Gr_r(H_m)\subset Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.

@@

\begin{lemma}
  \label{le:injective evaluation maps}
Let $m\geq 1$.  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

@@

\subsection{Truncated Preprojectives}
\label{sec:truncated preprojectives}
Following Lemma~\ref{le:injective evaluation maps}, we define the following.
\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and a surjective map
  \[\Ext(P_m,P_{m+1})\onto\Ext(P_m,P_{m+1}^V).\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
  The final claim follows from Remark~\ref{rem:reflection recursion}.
\end{proof}

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and a surjective map
  \[\Ext(P_{m+1},P_{m+1})\onto\Ext(P_{m+1},P_{m+1}^V).\]
  The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
  The rigidity of $P_{m+1}$ gives the final claim.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there is an isomorphism 
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

\begin{remark}
  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
\end{remark}

\begin{corollary}
  \label{cor:indecomposable truncated} 
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
\end{proof}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.\sayT{more details?}
\end{remark}

\begin{corollary}
  \label{cor:truncated preprojective isomorphism}
  Suppose $V\in Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

\begin{corollary}\sayT{proof?}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

>>>>

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
%Lemma~\ref{le:hom equivariance} gives an identification of $\Gr(H_m)$ with $\Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.

@@

\begin{lemma}
  \label{le:injective evaluation maps}
Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

@@

\subsection{Truncated Preprojectives}
\label{sec:truncated preprojectives}
Following Lemma~\ref{le:injective evaluation maps}, we define the following.
\begin{definition}
  For $V\in \Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and a surjective map
  \[\Ext(P_m,P_{m+1})\onto\Ext(P_m,P_{m+1}^V).\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
  The final claim follows from Remark~\ref{rem:reflection recursion}.
\end{proof}

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in \Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and a surjective map
  \[\Ext(P_{m+1},P_{m+1})\onto\Ext(P_{m+1},P_{m+1}^V).\]
  The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
  The rigidity of $P_{m+1}$ gives the final claim.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there is an isomorphism 
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

\begin{remark}
  The total Grassmannian $\Gr(H_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC \Gr(H_m)$ with objects the elements of $\Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(H_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(H_m)\cong\cP_{m+1}$.
\end{remark}

\begin{corollary}
  \label{cor:indecomposable truncated} 
  For $V\in \Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
\end{proof}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in \Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $\Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(H_m)^{op}\cong \Gr(H_m^*)$ with $\Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.\sayT{more details?}
\end{remark}

\begin{corollary}
  \label{cor:truncated preprojective isomorphism}
  Suppose $V\in \Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

\begin{corollary}\sayT{proof?}
  For $V,W\in \Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

\begin{lemma}
  \label{le:more truncated homomorphisms}
  For $W\in \Gr(H_m)$, $m\ge2$, the following hold:
  \begin{enumerate}
    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  By Lemma~\ref{le:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
